Optimizing Structural Properties Of Neural Networks With Genetic Algorithms

### 2015-08-02 paper/paper.tex
use contamination

A measure that is timeshift independent and maximized for functions of identical shape is the 
maximum of the cross correlation 
\begin{align}
    f\ix{c}(r, r') = \max_t \frac{\left<r, r'(\cdot - t)\right>}{\sqrt{\left< r, r\right> \left<r', r' \right>}}~.
\end{align}
Algorithmically, the signals are split into overlapping chunks which are correlated separately. 
This saves computational power and prevents minute differences in frequency to accumulate into 
a huge phase shift, i.e. the phase only has to remain relatively
constant over the timescale of a single chunk (about 10 seconds of simulated time).

@@

 On approach would be to use techniques from Monte Carlo Integration, e.g. stratified or importance sampling, to aid in the
evaluation of $E(F_C)$, but since $G(\lambda)$ depends noncontinuously on $\lambda$, it can only be applied to the dependence 
on the challenge $C$. This would mitigate the effects, but not solve the problem.

@@

In each iteration of the algorithm, a generation (set) of $N$ individuals (Generators) $G_t = \left\{ g_i \right\}$ is converted into
a new one $G_{t+1}$ according to the following scheme:
\begin{description}
 \item[Evaluation] The fitness $f_i = F_C(g_i)$ of each individual is mesasured using at least 20 samples (and adaptively more if the $f_i$ are spaced closely, to at msot 100).
 \item[Selection] All individuals are grouped into disjunct pairs for which we check which one has the higher $f$. This is repeated $K=10$ times, counting the wins of each individual. Based thereon we use the $p=50\%$ best individuals $S$ to build the next generation.

@@

- Hint / vague description of the codebase

>>>>

A measure that is time-shift independent and maximized for functions of identical shape is the 
maximum of the cross correlation 
\begin{align}
    f\ix{c}(r, r') = \max_t \frac{\left<r, r'(\cdot - t)\right>}{\sqrt{\left< r, r\right> \left<r', r' \right>}}~.
\end{align}
Algorithmically, the signals are split into overlapping chunks which are correlated separately. 
This saves computational power and prevents minute differences in frequency to accumulate into 
a huge phase shift, i.e. the phase only has to remain relatively
constant over the timescale of a single chunk (about 10 seconds of simulated time).

@@

 On approach would be to use techniques from Monte Carlo Integration, e.g. stratified or importance sampling, to aid in the
evaluation of $E(F_C)$, but since $G(\lambda)$ depends non-continuously on $\lambda$, it can only be applied to the dependence 
on the challenge $C$. This would mitigate the effects, but not solve the problem.

@@

In each iteration of the algorithm, a generation (set) of $N$ individuals (Generators) $G_t = \left\{ g_i \right\}$ is converted into
a new one $G_{t+1}$ according to the following scheme:
\begin{description}
 \item[Evaluation] The fitness $f_i = F_C(g_i)$ of each individual is measured using at least 20 samples (and adaptively more if the $f_i$ are spaced closely, to at msot 100).
 \item[Selection] All individuals are grouped into disjunct pairs for which we check which one has the higher $f$. This is repeated $K=10$ times, counting the wins of each individual. Based thereon we use the $p=50\%$ best individuals $S$ to build the next generation.

@@

\paragraph{Choice of Parameters}
